### 2015-08-17 manuscript/content/intro.tex
Intro. edits

\section{Introduction}
%%Describe the problem, state your contributions and the organization of the paper.T

@@

The Centers for Disease Control and Prevention (CDC) reported \cite{Schoenborn:2013} that between the years 2008 and 2010 roughly two-thirds of adults were current drinkers, but adults between the ages 18 and 24 were most commonly associated with consumption of more than 5 drinks in one day. There is also a known causal relationship between alcohol consumption and risky behaviors \cite{Assaad:2006}. One of the worst risky behaviors from drinking is drunk driving which is a persistent problem worldwide. Innocent people are harmed/killed in accidents where the driver was under the influence. It is reported by the Bureau of Transportation Statistics \cite{Chambers:2012} that in 2010 47.2\% of pedestrian fatalities and 39.9\% of vehicle occupant fatalities are caused by drunk driving.

Being able to calculate BAC is important for the portion of the population that consumes alcohol. Drinkers often find themselves in situations in which they are drinking but also need to plan on driving home. The issue comes when the drinker is not sure if they are sober enough, as in their BAC is below the legal limit, to drive home safely. In many cases, drinkers misjudge their intoxication, believing they will be able to safely get home, when actually their BAC is higher than the legal limit. While there are some ways available for people to measure their BAC, these methods are often invasive, inaccurate, or impractical.

The most commonly known method of measuring BAC is the use of a breathalyzer. These devices are portable, easily accessible, and accurate. However, breathalyzers have a stigma of DUI arrest, fines, and license suspension. Breathalyzers are also non-discreet and invasive because the device requires the user to blow into the device in order to measure BAC. Due to these reasons, people often do not want to use such a device. A noninvasive, discreet, and real-time method of measuring BAC is desired.

In this paper, we propose an android-based IoT middleware architecture and application for collecting sensor data on smartwatches and smartphones to predict BAC in real-time. A study conducted in Washington University \cite{Ward:2015} shows that electronic intervention programs are more successful at reducing college student drinking than general alcohol awareness program. By wearing a smartwatch, a user can be alerted in real time when the BAC is above certain level and programmed with different options of intervention when such an event occurs. For example, the application can send a text message to a trusted family member or friend or can lock the ignition of the car engine of the drinker. Currently, there are no known applications that leverages data from common wearable devices to predict BAC non-invasively and in real time.

The main contributions of the paper are:
\begin{itemize}
	\item A middleware platform that can collect data from any type of device (virtual or physical) that can communicate with android phones. 
	\item A BAC prediction model based on live smartwatch sensor data that enables users to get BAC measurement in real time.
	\item Geographical visualization of BAC predictions.
	\item Collection of a labeled BAC data set for training the prediction model.
\end{itemize}

%****Summary of the results and conclusion****

>>>>

\section{Introduction}
%% Domain introduction, problem, contributions, and organization of the paper.

@@

The Centers for Disease Control and Prevention (CDC) reported that between the years 2008 and 2010, roughly two-thirds of adults were drinkers, but adults between the ages 18 and 24 were most commonly associated with consumption of more than 5 drinks in one day \cite{Schoenborn:2013}. There is also a known causal relationship between alcohol consumption and risky behaviors \cite{Assaad:2006}. One of the most dangerous, worldwide (citation needed) problems of drinking is drunk driving. This problem is not only a hazard to the drunk drivers, but to pedestrians and other drivers. It is reported by the Bureau of Transportation Statistics that in 2010, 47.2\% of pedestrian fatalities and 39.9\% of vehicle occupant fatalities are caused by drunk driving \cite{Chambers:2012}.

Adults often find themselves on outings where they plan on drinking, but also on later driving home. At dangerous levels of intoxication, it can be difficult to judge ones own level of intoxication. Instead it would be better to get a definitive measurement; of the BAC, or simply a binary response, "drunk" or "not drunk." To do this, one can buy a breathalyzer and blow into it on every outing where drinking is involved. This is not a socially beneficial choice. The other option is to use a simple smartphone application to manually calculate BAC. However these demand a great deal of involvement from the user. To be practical, it would be useful to have some sort of non-invasive and accurate monitoring system that will warn its user if they become too intoxicated. A study conducted in Washington University shows that electronic intervention programs are more successful at reducing college student drinking than a general alcohol awareness program \cite{Ward:2015}. This system can also be used to warn friends and family, or prevent the operation of the user's car.

The main contributions of the paper are:

\begin{itemize}
	\item A machine learning model for the prediction of intoxication level from smartwatch sensor data.
	\item A general Android-based gateway system that can collect data from any type of physical or virtual sensor accessible by the host smartphone.
	\item An overall, sensor middleware system, including a geographic visualization service, that may be useful for answering many other important research questions.
\end{itemize}

%****Summary****
